\myTitle

### 2024-05-07 body-text-of-paper.tex
new changes

Because the simulations were done in a na\"{i}ve way that effectively assumes that the population
allele frequencies are identical to those observed in the samples themselves, we hypothesized that ADMIXTURE would return estimates of
$q_A$ that were
centered around the simulated values, even though samples $A$ and $B$ were drawn from the same
population. In other words, we expected to observe RISPI.
We further expected that ADMIXTURE would return more accurate estimates of the simulated
$q_A$ values when $N$ was smaller and the number of loci was larger.
We summarized the results by plotting boxplots of the ADMIXTURE-inferred $q_A$ values,
 for the 480 newly simulated individuals (and for the original samples, $A$ and $B$, in the
 case of unsupervised clustering),
for each combination of $L$, $N$, and $n$.

@@

In the \gscramble{} package there is a convenience function called {\footnotesize\tt create\_GSP()} that
will create GSPs for samples up to and including second-generation backcrosses (an example appears in Figure~\ref{fig:gsp2});
however, \gscramble{} is designed
to handle user-specified GSPs of arbitrary complexity.  When creating a unique GSP,
there are several requirements to ensure that the GSP is valid
and the simulation can execute successfully.
Writing $\founders$ for the set of all founder nodes, $\nonfound$ for the set of all non-founder nodes, and $\nonfounds$ for all non-founder
nodes that are not parents of other non-founders, but are adjacent to a sample node, $\nonfounde$ for all
non-founder nodes that have non-founder node daughters, but no sample nodes, and $\nonfoundse$ for all
non-founder nodes that are parents of non-founder nodes and also adjacent to sample-nodes, the necessary conditions
for a valid GSP, in addition to having no inbreeding loops, are:
\begin{equation}
\begin{aligned}
\sum_{x \in \nonfounds \cup \nonfoundse} S_x &= |\founders| &  \\
\sum_{i=1}^{e_x} G^-_{x,i} &= 2 & \forall x \in \founders \\
G^+_{x,1} &= G^+_{x,2} & \forall x \in \nonfound \\
\sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & \forall x \in \nonfounde  \\
 S_x/2  &= G^+_{x,1} +  G^+_{x,2} & ~~~\forall x \in \nonfounds \\
 S_x/2 + \sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & ~~~\forall x \in \nonfoundse.  \\
\end{aligned}
\end{equation}
In words, the separate lines above specify that 1) the number of samples
must equal the number of founders; 2) exactly two gametes must be
segregated from each founder; 3) the number of gametes incoming on each of the
two edges coming into a non-founder (from its parents) must be equal; 
4) the number of gametes going downward, out of a non-founder with no sample
daughters, must equal the number of gametes coming into that non-founder;
5)  the total number of gametes entering a non-founder with only sample daughters
must be half the number of sample daughters; and 6) the number of gametes
entering non-founders with both sample daughters and non-founder daughters must
equal half the number of its sample daughters plus the sum of the number of gametes segregated
along each edge to all of its non-founder daughters.

@@

The 160 invasive wild pig samples represented 120 reference individuals from the core regions of
3 populations (40 individuals each informed by previous analyses)
and 40 individuals from contact regions between these populations.
We used ADMIXTURE version 1.3.0 \citep{alexander2009fast} to characterize the genetic structure
of the 160 samples (for $K = {1...6}$). Using the 120 reference individuals identified to represent population cores,
we sought to contextualize the admixture patterns of the 40 samples
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated
pedigrees to represent the likely classes of admixed individuals that would be present in the samples
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were
$F_1$, $F_2$, $\BC_1$ and $\BC_2$ representing all two-population combinations
(Pop1 x Pop2, Pop1 x Pop3, Pop2 x Pop3, and reciprocally Pop2 x Pop1, Pop3 x Pop1, Pop3 x Pop2).
We also simulated individuals from each of the founder populations. The first step of this workflow involved
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{}
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed
individuals. Although we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}),
different numbers of simulated individuals are produced for each hybrid class. Therefore, for ease of simulating the exact number of desired individuals, we chose to simulate from
a single GSP for each of the hybrid classes by setting the corresponding hybrid category (i.e. {\tt F1}, {\tt F2}, etc.) parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE} with all others set to {\footnotesize\tt FALSE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()}  function to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of
21,000 simulated individuals.

@@

As expected, the perceived ability to estimate $q_A$ with ADMIXTURE was higher
for larger values of $L$ and for smaller values of $N$ (Figure~\ref{fig:bias-sims}).
%%%
\begin{figure*}
\newcommand{\biassimscap}{\footnotesize ADMIXTURE estimates of $q_A$ as described in
{\em An introductory motivating example}. In these results, the apparent ability to estimate $q_A$
is a bias resulting from the use of sampling with replacement to simulate new, admixed genotypes to
test in ADMIXTURE (e.g., these simulated samples suffer from RISPI).  ({\bf a}) Results from the supervised analysis in ADMIXTURE, where 
"ref-2" and "ref-1" show the $Q$-values estimated by ADMIXTURE for the reference samples
(even though they are treated by the program as being of known origin). ({\bf b}) Results for the
unsupervised analysis in ADMIXTURE. In both {\bf a} and {\bf b}, the different columns represent different numbers of markers
from 10 to 100,000, while different rows represent different original sample sizes, $N$, taken. Colors
of the boxplots indicate how many new individuals, $n$, of each $q_A$ value were simulated during each
replicate.}
\includegraphics[width=0.96\textwidth]{figures/bias-sims-unsup-and-sup.pdf}
\caption[\biassimscap]{\biassimscap}
\label{fig:bias-sims}
\end{figure*}
%%%
It is interesting to note
that, for numbers of loci,  $L$, that are 100 (or smaller) the effect is observed only when
sample size, $N$, is as small as 25---and even then the effect is slight.  However, when the
number of markers increases to 100,000---values that are becoming commonplace with the availability of chip-
or sequencing-based approaches---it is apparent that the sampling-with-replacement approach
induces an extreme bias.  With 100,000 markers, even if sample sizes ($N$) are as large as 250 individuals,
using na\"{i}ve simulations improperly indicates that admixture fractions of individuals can be
accurately estimated, even when there are no genetic differences, whatsoever between the populations that
samples $A$ and $B$ are drawn.

@@

As expected, there was no RISPI apparent in the ADMIXTURE-estimated
ancestry proportions  when simulating individuals
using \gscramble{} (Fig.~\ref{fig:norispi}).  On average, the estimated $Q$ values
were around 0.5, which is expected when the samples are drawn from the same
population.
%%%
\begin{figure}
\newcommand{\gssimcap}{\footnotesize ADMIXTURE estimates of ancestry
fractions, $Q$, for individuals simulated from samples from the same population,
simulated using \gscramble{}.  There is considerable variation in the estimates,
but the central tendency of them all is around 0.5, as would be expected in this case
within which the different
samples are drawn from the same population.  Contrast this to the corresponding panel ($L=1,000, N=50$) in Fig.~\ref{fig:bias-sims}(b),
in which the RISPI is readily apparent.}
\includegraphics[width=\columnwidth]{figures/gscram_supervised_Qs.pdf}
\caption[\gssimcap]{\gssimcap}
\label{fig:norispi}
\end{figure}
%%%

@@

The barplots in Fig.~\ref{fig:newhyb-sims-barplot} show the distribution of posterior
probabilities of the different hybrid categories. 
%%%%%%%%%%
\begin{figure}
\newcommand{\nhbpcap}{\footnotesize Posterior probabilities for simulated
individuals of different trout hybrid categories.  Each pair of plots shows the results
for individuals of the true hybrid category listed atop the pair  (see
 Table~\protect\ref{tab:newhybcats} for the meanings of the names).  The top panel of each pair
shows results for fish simulated with the 30 markers used by \protect\citet{rizza2023limited}, and the bottom panel shows results for fish simulated with the original 30 markers,
plus an additional  35 (65 total), some of which are linked
on the same chromosome. Each individual appears as a thin vertical line, posterior probabilities of
each inferred hybrid category are indicated by extent of different colors on those lines.  Individuals
are sorted according to maximum {\em a posteriori} hybrid category, and, within that by the
maximum posterior probability. }
{\centering
\includegraphics[width=0.98\columnwidth]{figures/newhybs-texed-crop.pdf}
}
\caption[\nhbpcap]{\nhbpcap}
\label{fig:newhyb-sims-barplot}
\end{figure}
%%%%%%%%%%
These are similar to STRUCTURE or ADMIXTURE barplots;
however, rather than plotting the ancestry fraction, the different colors are showing the
posterior probabilities of different hybrid categories.  Each individual is represented by a thin
vertical line, and the individuals have been arranged from left to right and the colors have been
arranged from top to bottom throughout different sections of the plot to make it easy to see
the patterns.  The {\em maximum-a-posteriori} (MAP) hybrid category for any individual is represented
by the color that is on the bottom of the bar, so it is easy to see the shifts where the MAP hybrid
category changes from one to another.  It is apparent over all individuals simulated to be
either CCT, $F_1$, $F_2$, $BC_1$--CCT, or $BC_2$--CCT, that the MAP estimate of their
hybrid categories were correct for largely the same number of individuals whether 30 or 65 markers
were used. By contrast, for the individuals simulated to be of the complex hybrid category
$BC_1$--CCT~$\times$~$BC_2$--CCT, the MAP estimate from 65 markers was correct more often 
than from 
30 markers.  However, it is also apparent that using 65 markers, some of which are physically
linked, in the software {\em NewHybrids}---which assumes that all markers are unlinked---yields 
estimates of uncertainty that are inaccurate.  Tellingly, when the estimates using 65 markers are 
incorrect (for example, when $BC_1$--CCT individuals have a maximum posterior of being in the 
$BC_2$--CCT category,
or when individuals that are truly of the $BC_1$--CCT~$\times$~$BC_2$--CCT category have a
maximum posterior of being from the $BC_2$--CCT category), many of those incorrect posteriors
are quite high ($>0.90$).  In fact, using 65 markers yields more incorrect {\em and high} posteriors 
than does using the 30 unlinked markers. So, as expected, ignoring physical linkage the way
{\sc NewHybrids} does can yield a poor estimate of the uncertainty around different inferences.

@@

Here, we present \gscramble{}, a simulation approach for creating biologically informed individual 
genotypes of different hybrid classes. Two integral features of \gscramble{} are: 
1) alleles are sampled from populations without replacement and 
2) alleles are segregated based on species-specific recombination rates. 
Our results show that both 
of these features are especially important for accurately reflecting empirical data from large genetic 
marker sets (thousands of markers), 
which are common from  both custom SNP-chip genotyping and next generation sequencing methods. Sampling alleles without 
replacement, and thereby preserving the genetic differences (or lack thereof) of populations is 
essential for avoiding RISPI---an issue that is exacerbated as the number of 
alleles sampled for an individual increases. Additionally, we show the importance of accounting for 
the physical linkage of markers when large marker sets are used and that treating loci as 
independent results in erroneously reduced variation in the admixture 
fractions of simulated individuals.

\gscramble{} is conducive for numerous types of contemporary marker data sets. As mentioned above, 
one key feature of \gscramble{} is the integration of recombination rates, thereby accounting for physical 
linkage which is expected among larger contemporary data sets. Furthermore, \gscramble{} performs marker 
segregation with computational efficiency---for the four different GSPs used with the invasive wild pig data set, 
the mean run time of each simulation with 14,233 SNP loci was 2.3 seconds (range: 1.9-5.7 $s$). 
While \gscramble{} is equally applicable to data sets with 
microhaplotypes \citep{baetscher2018microhaplotypes} or microsatellites \citep{zhan2017megasat}, 
it is not suited for genotype likelihood data (i.e. from low-coverage whole genome sequencing). 
The \gscramble{} simulation approach involves the segregation of gametes and therefore requires 
that genotypes are resolved.

We envision \gscramble{} to be relevant for a diverse range of potential applications. In our 
provided empirical examples with trout and wild pig data, we demonstrate the basics of 
creating hybrid classes. Similarly, \gscramble{} has recently been used to demonstrate the 
power for hybrid classification of a population genetics method used to differentiate wild pigs with 
wildboar introgression from domestic pigs \citep{smyser2024probgen}. In \citet{smyser2024probgen}, 
researchers made use of the segregation options in \gscramble{} in order to preserve founder individuals' 
genotypes within populations (in contrast to \textit{a priori} shuffling alleles within populations) in order to 
retain the subpopulation structure present within certain populations---thereby, better reflecting the 
actual admixture variation expected from wildboar and domestic pig hybrids. We think \gscramble{} 
may also be useful for assessing relatedness estimates using pedigrees of varying complexity. Here, it 
is important to note that each time a gamete is segregated in a GSP, its complement is also 
segregated---an example of antithetical variate sampling in Monte Carlo methods. Thus, in the 
example of relatedness, fixed specified founders should be repeatedly "mated" with one offspring 
sampled per iteration to avoid sampling of anticorrelated genotypes.

>>>>

Because the simulations were done in a na\"{i}ve way that effectively assumes that the population
allele frequencies are identical to those observed in the samples themselves, we hypothesized that ADMIXTURE would return estimates of
$q_A$ that were
centered around the simulated values, even though samples $A$ and $B$ were drawn from the same
population. In other words, we expected to observe RISPI.
We further expected that ADMIXTURE would return more accurate estimates of the simulated
$q_A$ values when $N$ was smaller and the number of loci was larger - 
attributes that magnify the effect of RISPI.
We summarized the results with boxplots of the ADMIXTURE-inferred $q_A$ values,
 for the 480 newly simulated individuals (and for the original samples, $A$ and $B$, in the
 case of unsupervised clustering),
for each combination of $L$, $N$, and $n$.

@@

In the \gscramble{} package there is a convenience function called {\footnotesize\tt create\_GSP()} that
will create GSPs for samples up to and including second-generation backcrosses (an example appears in Figure~\ref{fig:gsp2});
however, \gscramble{} is designed
to handle user-specified GSPs of arbitrary complexity.  When creating a unique GSP,
there are several requirements to ensure that the GSP is valid
and the simulation can execute successfully.
Writing $\founders$ for the set of all founder nodes, $\nonfound$ for the set of all non-founder nodes, and $\nonfounds$ for all non-founder
nodes that are not parents of other non-founders, but are adjacent to a sample node, $\nonfounde$ for all
non-founder nodes that have non-founder node daughters, but no sample nodes, and $\nonfoundse$ for all
non-founder nodes that are parents of non-founder nodes and also adjacent to sample-nodes, the necessary conditions
for a valid GSP, in addition to having no inbreeding loops, are:
\begin{equation}
\begin{aligned}
\sum_{x \in \nonfounds \cup \nonfoundse} S_x &= |\founders| &  \\
\sum_{i=1}^{e_x} G^-_{x,i} &= 2 & \forall x \in \founders \\
G^+_{x,1} &= G^+_{x,2} & \forall x \in \nonfound \\
\sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & \forall x \in \nonfounde  \\
 S_x/2  &= G^+_{x,1} +  G^+_{x,2} & ~~~\forall x \in \nonfounds \\
 S_x/2 + \sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & ~~~\forall x \in \nonfoundse.  \\
\end{aligned}
\end{equation}
In words, the separate lines above specify that 1) the number of samples
must equal the number of founders; 2) exactly two gametes must be
segregated from each founder; 3) the number of gametes to a non-founder along the 
edges from its parents must be equal; 
4) the number of gametes going downward, out of a non-founder with no sample
daughters, must equal the number of gametes coming into that non-founder;
5)  the total number of gametes entering a non-founder with only sample daughters
must be half the number of sample daughters; and 6) the number of gametes
entering non-founders with both sample daughters and non-founder daughters must
equal half the number of its sample daughters plus the sum of the number of gametes segregated
along each edge to all of its non-founder daughters.

@@

The 160 invasive wild pig samples represented 120 reference individuals from the core regions of
3 populations (40 individuals each informed by previous analyses)
and 40 individuals from contact regions between these populations.
We used ADMIXTURE version 1.3.0 \citep{alexander2009fast} to characterize the genetic structure
of the 160 samples (for $K = {1...6}$). Using the 120 reference individuals identified to represent population cores,
we sought to contextualize the admixture patterns of the 40 samples
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated
pedigrees to represent the likely classes of admixed individuals that would be present in the samples
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were
$F_1$, $F_2$, $\BC_1$ and $\BC_2$ representing all two-population combinations
(Pop1 x Pop2, Pop1 x Pop3, Pop2 x Pop3, and reciprocally Pop2 x Pop1, Pop3 x Pop1, Pop3 x Pop2).
We also simulated individuals from each of the founder populations. The first step of this workflow involved
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{}
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed
individuals. Although we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}),
different numbers of simulated individuals are produced for each hybrid class. Therefore, for ease of simulating the exact number of desired individuals, we chose to simulate from
a single GSP for each of the hybrid classes by setting the corresponding hybrid category (i.e., {\tt F1}, {\tt F2}, etc.) parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE} with all others set to {\footnotesize\tt FALSE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()}  function to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of
21,000 simulated individuals.

@@

As expected, the perceived ability to estimate $q_A$ with ADMIXTURE was higher
for larger values of $L$ and for smaller values of $N$ (Figure~\ref{fig:bias-sims}).
%%%
\begin{figure*}
\newcommand{\biassimscap}{\footnotesize ADMIXTURE estimates of $q_A$ as described in
{\em An introductory motivating example}. In these results, the apparent ability to estimate $q_A$
is a bias resulting from the use of sampling with replacement to simulate new, admixed genotypes to
test in ADMIXTURE (e.g., these simulated samples suffer from RISPI).  ({\bf a}) Results from the supervised analysis in ADMIXTURE, where 
"ref-2" and "ref-1" show the $Q$-values estimated by ADMIXTURE for the reference samples
(even though they are treated by the program as being of known origin). ({\bf b}) Results for the
unsupervised analysis in ADMIXTURE. In both {\bf a} and {\bf b}, the different columns represent different numbers of markers
from 10 to 100,000, while different rows represent different original sample sizes, $N$, taken. Colors
of the boxplots indicate how many new individuals, $n$, of each $q_A$ value were simulated during each
replicate.}
\includegraphics[width=0.96\textwidth]{figures/bias-sims-unsup-and-sup.pdf}
\caption[\biassimscap]{\biassimscap}
\label{fig:bias-sims}
\end{figure*}
%%%
It is interesting to note
that, for numbers of loci,  $L$, that are 100 (or smaller) the effect is observed only when
sample size, $N$, is as small as 25---and even then the effect is slight.  However, when the
number of markers increases to 100,000---values that are becoming commonplace with the availability of chip-
or sequencing-based approaches---it is apparent that the sampling-with-replacement approach
induces an extreme bias.  With 100,000 markers, even if sample sizes ($N$) are as large as 250 individuals,
using na\"{i}ve simulations improperly indicates that admixture fractions of individuals can be
accurately estimated, even when there are no genetic differences between the populations from which
samples $A$ and $B$ are drawn.

@@

As expected, there was no observed RISPI in the ADMIXTURE-estimated
ancestry proportions  when simulating individuals
using \gscramble{} (Fig.~\ref{fig:norispi}).  On average, the estimated $Q$ values
were around 0.5, which is expected when the samples are drawn from the same
population.
%%%
\begin{figure}
\newcommand{\gssimcap}{\footnotesize ADMIXTURE estimates of ancestry
fractions, $Q$, for individuals simulated from samples from the same population,
simulated using \gscramble{}.  There is considerable variation in the estimates,
but the central tendency of them all is around 0.5, as would be expected in this case
within which the different
samples are drawn from the same population.  Contrast this to the corresponding panel ($L=1,000, N=50$) in Fig.~\ref{fig:bias-sims}(b),
in which the RISPI is readily apparent.}
\includegraphics[width=\columnwidth]{figures/gscram_supervised_Qs.pdf}
\caption[\gssimcap]{\gssimcap}
\label{fig:norispi}
\end{figure}
%%%

@@

The barplots in Fig.~\ref{fig:newhyb-sims-barplot} show the distribution of posterior
probabilities of the different hybrid categories. 
%%%%%%%%%%
\begin{figure}
\newcommand{\nhbpcap}{\footnotesize Posterior probabilities for simulated
individuals of different trout hybrid categories.  Each pair of plots shows the results
for individuals of the true hybrid category listed atop the pair  (see
 Table~\protect\ref{tab:newhybcats} for the meanings of the names).  The top panel of each pair
shows results for fish simulated with the 30 markers used by \protect\citet{rizza2023limited}, and the bottom panel shows results for fish simulated with the original 30 markers,
plus an additional  35 (65 total), some of which are linked
on the same chromosome. Each individual appears as a thin vertical line, posterior probabilities of
each inferred hybrid category are indicated by extent of different colors on those lines.  Individuals
are sorted according to maximum {\em a posteriori} hybrid category, and, within that by the
maximum posterior probability. }
{\centering
\includegraphics[width=0.98\columnwidth]{figures/newhybs-texed-crop.pdf}
}
\caption[\nhbpcap]{\nhbpcap}
\label{fig:newhyb-sims-barplot}
\end{figure}
%%%%%%%%%%
These are similar to STRUCTURE or ADMIXTURE barplots;
however, rather than plotting the ancestry fraction, the different colors are showing the
posterior probabilities of different hybrid categories.  Each individual is represented by a thin
vertical line, and the individuals have been arranged from left to right and the colors have been
arranged from top to bottom throughout different sections of the plot to make it easy to see
the patterns.  The {\em maximum-a-posteriori} (MAP) hybrid category for any individual is represented
by the color that is on the bottom of the bar, so it is easy to see the shifts where the MAP hybrid
category changes from one to another.  It is apparent over all individuals simulated to be
either CCT (cut-throat trout), $F_1$, $F_2$, $BC_1$--CCT, or $BC_2$--CCT, that the MAP estimate of their
hybrid categories were correct for largely the same number of individuals whether 30 or 65 markers
were used. By contrast, for the individuals simulated to be of the complex hybrid category
$BC_1$--CCT~$\times$~$BC_2$--CCT, the MAP estimate from 65 markers was correct more often 
than from 
30 markers.  However, it is also apparent that using 65 markers, some of which are physically
linked, in the software {\em NewHybrids}---which assumes that all markers are unlinked---yields 
estimates of uncertainty that are inaccurate.  Tellingly, when the estimates using 65 markers are 
incorrect (for example, when $BC_1$--CCT individuals have a maximum posterior of being in the 
$BC_2$--CCT category,
or when individuals that are truly of the $BC_1$--CCT~$\times$~$BC_2$--CCT category have a
maximum posterior of being from the $BC_2$--CCT category), many of those incorrect posteriors
are quite high ($>0.90$).  In fact, using 65 markers yields more incorrect {\em and high} posteriors 
than does using the 30 unlinked markers. So, as expected, ignoring physical linkage (e.g., as 
implemented in {\sc NewHybrids}) 
can yield a poor estimate of the uncertainty around different inferences.

@@

Here, we present \gscramble{}, a simulation approach for creating biologically informed individual 
genotypes of different hybrid classes. Two integral features of \gscramble{} are: 
1) alleles are sampled from populations without replacement and 
2) alleles are segregated based on species-specific recombination rates. 
Our results show that both 
of these features are especially important for accurately reflecting empirical data from large genetic 
marker sets (thousands of markers), 
which are common from  both custom SNP-chip genotyping and next generation sequencing methods. Sampling alleles without 
replacement, and thereby preserving the genetic differences (or lack thereof) of populations is 
essential for avoiding RISPI---an issue that is exacerbated as the number of 
alleles sampled for an individual increases. Additionally, we demonstrate the importance of accounting for 
the physical linkage of markers when large marker sets are used and that treating physically linked loci as 
independent erroneously reduces the variation in the admixture 
fractions of simulated individuals.

\gscramble{} is conducive for analysis of numerous types of marker sets available from contemporary data generation 
techniques. As mentioned above, 
one key feature of \gscramble{} is the integration of recombination rates, thereby accounting for physical 
linkage which is expected among larger contemporary data sets. Furthermore, \gscramble{} performs marker 
segregation with computational efficiency---for the four different GSPs used with the invasive wild pig data set, 
the mean run time of each simulation with 14,233 SNP loci was 2.3 seconds (range: 1.9-5.7 $s$). 
While \gscramble{} is equally applicable to data sets with 
microhaplotypes \citep{baetscher2018microhaplotypes} or microsatellites \citep{zhan2017megasat}, 
it is not suited for genotype likelihood data (i.e. from low-coverage whole genome sequencing). 
Specifically, simulations conducted within \gscramble{} involve the segregation of gametes within the 
specified pedigrees and, therefore, requires genotypes to be resolved.

We envision \gscramble{} to be relevant for a diverse range of potential applications. In our 
provided empirical examples with trout and wild pig data, we demonstrate the basics of 
creating hybrid classes. In much the same manner, \gscramble{} has been used to evaluate the statistical power 
of hybrid classification used to differentiate wild boar hybrids from domestic pigs 
\citep{smyser2024probgen}. Specifically \citet{smyser2024probgen} used the segregation options in \gscramble{} 
 to preserve founder individuals' genotypes within populations in contrast to \textit{a priori} shuffling alleles 
within populations. This retains the subpopulation structure present within certain populations---thereby, better reflecting the 
actual admixture variation expected from wild boar and domestic pig hybrids. We think \gscramble{} 
may also be useful for assessing relatedness estimates using pedigrees of varying complexity. Here, it 
is important to note that each time a gamete is segregated in a GSP, its complement is also 
segregated---an example of antithetical variate sampling in Monte Carlo methods. Thus, in the 
example of relatedness, fixed specified founders should be repeatedly "mated" with one offspring 
sampled per iteration to avoid sampling of anticorrelated genotypes.
